---
title: "Part 1-Simulation Exercise"
author: "Harikrishna Vemula"
date: "10/13/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{R echo=TRUE, warning=FALSE,message=FALSE}
library(knitr)
library(ggplot2)
```

## Overview

This is part 1 assignment on Simulation Exercise using R. This Simulation Exercise intension is, investigating the exponential distribution and compare it with the Central Limit Theorem. 

## Simulations
initializing variables lambda, seed, n and n's simulation.
```{r}
ECHO=TRUE
set.seed(1337)
lambda = 0.2
n = 40
nsm = 1000
```
Calculating mean for 1000 samples of 40 exponentials

```{r}
ex <- replicate(nsm, rexp(n, lambda))
exp_means <- apply(ex, 2, mean)
```

## 1.Sample Mean versus Theoretical Mean
#### Sample Mean
Calculating the mean .
```{r}
mean(exp_means)
```

#### Theoretical Mean
Calculating theoretical mean.
```{r}
lambda^-1
```

#### Difference
sample mean Vs exponential distribution theoretical mean.
```{r}
abs(mean(exp_means)-lambda^-1)
```

## 2.Sample Variance versus Theoretical Variance
#### Sample Variance
Calculating sample variance
variance.
```{r}
var(exp_means)
```

#### Theoretical Variance
Calculating theoretical variance
```{r}
(lambda * sqrt(n))^-2
```

#### Difference
Sample Variance Vs Theoretical Variance
```{r}
abs(var(exp_means)-(lambda * sqrt(n))^-2)
```

## Distribution
The following graph illustrates histogram for 1000 simulations.
```{r}
library(ggplot2)
ggplot(data.frame(y=exp_means), aes(x=y)) + 
  geom_histogram(aes(y=..density..), binwidth=0.2, fill="blue",color="red") +  
  stat_function(fun=dnorm, args=list(mean=lambda^-1,sd=(lambda*sqrt(n))^-1), 
                size=2) +
  labs(title="Simulations", x="Mean")


```